---
title: "The Future of Entertainment Marketing"
subtitle: "Data-Driven Strategies for the Streaming Era"
author: "Kelly Liang"
date: today
format:
  revealjs:
    theme: [default, presentation-theme.scss]
    slide-number: true
    transition: fade
    background-transition: fade
    footer: "Kelly Liang · Entertainment Marketing Portfolio"
    progress: true
    width: 1280
    height: 720
    fig-align: center
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup

library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(forcats)

navy       <- "#0A1628"
navy_light <- "#1E3060"
gold       <- "#C9A84C"
gray_text  <- "#6B7280"
white      <- "#FFFFFF"
grid_dark  <- "#2a3f5f"

theme_slide_dark <- function() {
  theme_minimal(base_family = "sans", base_size = 13) +
  theme(
    plot.background    = element_rect(fill = "transparent", color = NA),
    panel.background   = element_rect(fill = "transparent", color = NA),
    panel.grid.minor   = element_blank(),
    panel.grid.major   = element_line(color = grid_dark, linewidth = 0.4),
    axis.text          = element_text(color = white, size = 11),
    axis.title         = element_text(color = white, size = 11),
    legend.background  = element_rect(fill = "transparent", color = NA),
    legend.key         = element_rect(fill = "transparent", color = NA),
    legend.text        = element_text(color = white, size = 10),
    legend.title       = element_blank(),
    plot.title         = element_text(color = gold, size = 14, face = "bold",
                                      margin = margin(b = 8)),
    plot.caption       = element_text(color = gray_text, size = 9),
    plot.margin        = margin(8, 12, 8, 12)
  )
}
```

# Industry Landscape {background-color="#0A1628"}

[MARKET OVERVIEW]{style="font-size:0.7rem;letter-spacing:3px;color:#C9A84C;"}

```{r}
#| label: streaming-trend
#| fig-width: 7
#| fig-height: 3.2

trend_df <- tibble(
  Year    = c(2020, 2021, 2022, 2023, 2024),
  Revenue = c(13.4, 15.9, 17.5, 19.1, 20.8)
)

ggplot(trend_df, aes(x = Year, y = Revenue)) +
  geom_area(fill = gold, alpha = 0.18) +
  geom_line(color = gold, linewidth = 1.8) +
  geom_point(color = gold, size = 4, fill = navy, shape = 21, stroke = 2) +
  geom_text(aes(label = paste0("$", Revenue, "B")),
            vjust = -1.2, color = white, size = 3.8, fontface = "bold") +
  scale_x_continuous(breaks = trend_df$Year) +
  scale_y_continuous(labels = label_dollar(suffix = "B"),
                     limits = c(10, 25),
                     expand = expansion(mult = c(0, 0.05))) +
  labs(title = "Global Streaming Revenue ($B)",
       subtitle = "Music streaming crossed $20B in 2024 — up 55% since 2020",
       x = NULL, y = NULL) +
  theme_slide_dark() +
  theme(
    panel.grid.major.x = element_blank(),
    plot.subtitle = element_text(color = gray_text, size = 11, margin = margin(b = 6))
  )
```

::: {style="display:grid;grid-template-columns:repeat(4,1fr);gap:0.75rem;margin-top:0.5rem;"}
::: {style="background:rgba(201,168,76,0.1);border:1px solid rgba(201,168,76,0.3);border-radius:4px;padding:0.6rem;text-align:center;"}
[**$20B**]{style="color:#C9A84C;font-size:1.2rem;font-weight:700;"} [Global streaming revenue]{style="color:rgba(255,255,255,0.6);font-size:0.72rem;display:block;"}
:::
::: {style="background:rgba(201,168,76,0.1);border:1px solid rgba(201,168,76,0.3);border-radius:4px;padding:0.6rem;text-align:center;"}
[**+32%**]{style="color:#C9A84C;font-size:1.2rem;font-weight:700;"} [Podcast YoY growth 18–34]{style="color:rgba(255,255,255,0.6);font-size:0.72rem;display:block;"}
:::
::: {style="background:rgba(201,168,76,0.1);border:1px solid rgba(201,168,76,0.3);border-radius:4px;padding:0.6rem;text-align:center;"}
[**78%**]{style="color:#C9A84C;font-size:1.2rem;font-weight:700;"} [Gen Z discover via social]{style="color:rgba(255,255,255,0.6);font-size:0.72rem;display:block;"}
:::
::: {style="background:rgba(201,168,76,0.1);border:1px solid rgba(201,168,76,0.3);border-radius:4px;padding:0.6rem;text-align:center;"}
[**$31B**]{style="color:#C9A84C;font-size:1.2rem;font-weight:700;"} [Live events market rebound]{style="color:rgba(255,255,255,0.6);font-size:0.72rem;display:block;"}
:::
:::

# Audience Segmentation {background-color="#132040"}

[ANALYTICS]{style="font-size:0.7rem;letter-spacing:3px;color:#C9A84C;"}

### Three High-Value Listener Clusters

```{r}
#| label: segment-chart
#| fig-width: 10
#| fig-height: 3.6

segments <- tibble(
  Segment   = c("Discovery Seekers", "Loyalists", "Casual Streamers"),
  Share     = c(25, 42, 33),
  Avg_Hours = c(4.2, 3.1, 1.8),
  Conv_Rate = c(5.1, 6.8, 2.4)
)

seg_long <- segments |>
  pivot_longer(c(Share, Avg_Hours, Conv_Rate),
               names_to  = "Metric",
               values_to = "Value") |>
  mutate(
    Metric  = recode(Metric,
                     "Share"     = "Audience Share (%)",
                     "Avg_Hours" = "Daily Streaming Hrs",
                     "Conv_Rate" = "Conversion Rate (%)"),
    Segment = factor(Segment,
                     levels = c("Discovery Seekers", "Loyalists", "Casual Streamers"))
  )

pal_seg <- c(
  "Discovery Seekers" = navy_light,
  "Loyalists"         = gold,
  "Casual Streamers"  = "#64748b"
)

ggplot(seg_long, aes(x = Segment, y = Value, fill = Segment)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = Value),
            vjust = -0.5, color = white, size = 4, fontface = "bold") +
  scale_fill_manual(values = pal_seg) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.22))) +
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = NULL, y = NULL) +
  theme_slide_dark() +
  theme(
    strip.text         = element_text(color = gold, size = 11, face = "bold"),
    strip.background   = element_rect(fill = "transparent", color = NA),
    panel.grid.major.x = element_blank(),
    axis.text.x        = element_text(size = 10)
  )
```

# Platform Strategy {background-color="#0A1628"}

[STRATEGY]{style="font-size:0.7rem;letter-spacing:3px;color:#C9A84C;"}

### Where to Invest: Reach vs Engagement

```{r}
#| label: platform-chart
#| fig-width: 10
#| fig-height: 3.8

platform_df <- tibble(
  Platform = c("TikTok", "Instagram", "YouTube", "Twitter/X", "Spotify Ads"),
  Reach_K  = c(310, 280, 140, 90, 95),
  Eng_Rate = c(9.1, 7.4, 5.6, 4.2, 3.8),
  CPA      = c(1.80, 2.10, 3.40, 5.10, 4.20)
) |>
  mutate(
    fill_col = case_when(
      Platform == "TikTok"    ~ gold,
      Platform == "Instagram" ~ navy_light,
      TRUE                    ~ "#475569"
    )
  )

ggplot(platform_df,
       aes(x = Reach_K, y = Eng_Rate,
           size  = 1 / CPA,
           color = fill_col,
           label = Platform)) +
  geom_point(alpha = 0.85) +
  geom_text(vjust = -1.4, color = white, size = 3.8, fontface = "bold") +
  scale_color_identity() +
  scale_size_continuous(range = c(6, 20), guide = "none") +
  scale_x_continuous(labels = label_comma(suffix = "K"),
                     expand = expansion(mult = c(0.05, 0.1))) +
  scale_y_continuous(labels = label_percent(scale = 1),
                     expand = expansion(mult = c(0.1, 0.25))) +
  labs(
    title    = "Platform Reach vs. Engagement Rate",
    subtitle = "Bubble size = cost efficiency (larger = lower CPA = better ROI)",
    x = "Monthly Reach (thousands)", y = "Engagement Rate (%)"
  ) +
  theme_slide_dark() +
  theme(plot.subtitle = element_text(color = gray_text, size = 10, margin = margin(b = 6)))
```

# Campaign Results {background-color="#132040"}

[OUTCOMES]{style="font-size:0.7rem;letter-spacing:3px;color:#C9A84C;"}

### Streaming Platform Launch · Before vs After

```{r}
#| label: results-chart
#| fig-width: 9
#| fig-height: 3.5

results_df <- tibble(
  Metric = c("Brand Awareness", "App Downloads",
             "Social Followers", "Trial Sign-ups"),
  Before = c(12, 0, 5, 0),
  After  = c(47, 84, 38, 62)
) |>
  pivot_longer(c(Before, After),
               names_to  = "Period",
               values_to = "Value") |>
  mutate(
    Metric = factor(Metric, levels = c("Brand Awareness", "App Downloads",
                                       "Social Followers", "Trial Sign-ups")),
    Period = factor(Period, levels = c("Before", "After"))
  )

ggplot(results_df, aes(x = Value, y = Metric, fill = Period)) +
  geom_col(position = "dodge", width = 0.6) +
  geom_text(aes(label = paste0(Value, "%")),
            position = position_dodge(width = 0.6),
            hjust = -0.15, color = white, size = 3.8, fontface = "bold") +
  scale_fill_manual(values = c("Before" = "#475569", "After" = gold)) +
  scale_x_continuous(limits = c(0, 105),
                     expand = expansion(mult = c(0, 0.02)),
                     labels = label_percent(scale = 1)) +
  labs(title = "Before vs. After Campaign (% of goal)", x = NULL, y = NULL) +
  theme_slide_dark() +
  theme(panel.grid.major.y = element_blank(), legend.position = "top")
```

::: {style="display:grid;grid-template-columns:1fr 1fr;gap:1rem;margin-top:0.25rem;font-size:0.85rem;"}
::: {}
✅ **40%** brand awareness lift in target demo  
✅ Cost per acquisition: **$2.10** (goal was $3.00)
:::
::: {}
✅ **500K+** combined influencer reach  
⚠️ Twitter/X budget reallocated to TikTok in Week 3
:::
:::

# Recommendations {background-color="#0A1628"}

[NEXT STEPS]{style="font-size:0.7rem;letter-spacing:3px;color:#C9A84C;"}

### Prioritized Investment by Expected ROI

```{r}
#| label: recommendations-chart
#| fig-width: 9
#| fig-height: 3.8

recs_df <- tibble(
  Action    = c("TikTok-First Content", "Creator Partnerships",
                "Hybrid Live Events",   "Spotify Editorial",
                "First-Party Data",     "AI Email Personalization"),
  ROI_Score = c(9.2, 8.5, 8.0, 7.8, 7.1, 6.4),
  Effort    = c("Low", "Medium", "High", "Low", "High", "Medium"),
  Timeline  = c("0–3 mo", "0–3 mo", "12–18 mo",
                "3–6 mo", "6–12 mo", "6–12 mo")
) |>
  mutate(
    Action   = fct_reorder(Action, ROI_Score),
    fill_col = case_when(
      Effort == "Low"    ~ gold,
      Effort == "Medium" ~ navy_light,
      TRUE               ~ "#475569"
    )
  )

ggplot(recs_df, aes(x = ROI_Score, y = Action, fill = fill_col)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(ROI_Score, " / 10  ·  ", Timeline)),
            hjust = -0.08, color = white, size = 3.5, fontface = "bold") +
  scale_fill_identity() +
  scale_x_continuous(limits = c(0, 12), expand = expansion(mult = c(0, 0.02))) +
  labs(
    title   = "Recommended Actions by Expected ROI Score",
    caption = "Gold = Low effort  |  Navy = Medium effort  |  Gray = High effort",
    x = "ROI Score (out of 10)", y = NULL
  ) +
  theme_slide_dark() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(color = grid_dark, linewidth = 0.4)
  )
```

# Thank You {background-color="#0A1628" visibility="uncounted"}

::: {style="text-align:center;padding-top:3rem;"}

[Let's talk entertainment marketing]{style="color:rgba(255,255,255,0.6);font-size:1.1rem;display:block;margin-top:0.5rem;"}

<!-- Replace with your actual email and LinkedIn -->
[your.email@email.com]{style="color:#C9A84C;font-size:1rem;display:block;margin-top:2.5rem;letter-spacing:1px;"}
[linkedin.com/in/yourprofile]{style="color:#C9A84C;font-size:1rem;display:block;margin-top:0.4rem;letter-spacing:1px;"}

:::
